\textbf{ Interpretable Gaussian Processes for Stellar Variability }

### 2020-12-07 tex/gitlinks.tex
added limb darkening; still needs testing

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/1ceb09cbd12c72831cc9ea7579c67ae74c9220eb/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/1ceb09cbd12c72831cc9ea7579c67ae74c9220eb/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/1ceb09cbd12c72831cc9ea7579c67ae74c9220eb/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/a27b8de7b8ca0c6ba3f072e82097cd00d7a6e643/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/a27b8de7b8ca0c6ba3f072e82097cd00d7a6e643/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/a27b8de7b8ca0c6ba3f072e82097cd00d7a6e643/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

### 2020-12-07 tex/ms.tex
added limb darkening; still needs testing

\subsection{With limb darkening}
%
\xxx{TODO.}

>>>>

\subsection{With limb darkening}
%
\label{sec:ld}
We must adjust our expression for the flux in the presence of limb darkening.
For any polynomial limb darkening law of the form
%
\begin{align}
    \label{eq:ld:I}
    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
    \quad,
\end{align}
%
where $I$ is the intensity on the stellar surface,
$\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the
projected disk, and $u_n$ is a limb darkening coefficient, the effect of
limb darkening on the stellar map can be expressed exactly as a linear
operation on the spherical harmonic coefficient vector
\citep{Luger2019}.
This includes the popular linear and quadractic limb darkening laws
and generalizes to \emph{any} limb darkening law in the limit
$n_\mathrm{max} \rightarrow \infty$. The linearity of the problem
can be understood by noting that all terms
in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$,
all of which can be expressed exactly as sums of spherical harmonics
\citep{Luger2019}. When weighting the surface intensity by the limb darkening
profile, the resulting intensity is simply a product of spherical harmonics,
which is itself a linear combination of spherical harmonics.
Thus, given a limb darkening law
of degree $n_\mathrm{max}$ with coefficients $\mathbf{u}$,
we can construct a matrix $\mathbf{L}(\mathbf{u})$
that transforms a spherical harmonic vector $\mathbf{y}$ of degree
$l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\mathbf{y'}$
of degree $l_\mathrm{max} + n_\mathrm{max}$. As an example, consider
a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law
($n_\mathrm{max} = 1$) with coefficient vector $\mathbf{u} = ( u_1 )$.
The transformation matrix from $\mathbf{y}$ to $\mathbf{y'}$ is
%
\begin{proof}{}
    \label{eq:ld:L}
    \setstackgap{L}{1.5\baselineskip}
    \mathbf{L}(\mathbf{u}) =
    \frac{1}{1 - \frac{u_1}{3}}
    \begin{pmatrix}
        \quadquad1-u_1\quadquad & 0                       & \frac{u_1}{\sqrt{3}}    & 0                       \\
        0                       & \quadquad1-u_1\quadquad & 0                       & 0                       \\
        \frac{u_1}{\sqrt{3}}    & 0                       & \quadquad1-u_1\quadquad & 0                       \\
        0                       & 0                       & 0                       & \quadquad1-u_1\quadquad \\
        0                       & 0                       & 0                       & 0                       \\
        0                       & \frac{u_1}{\sqrt{5}}    & 0                       & 0                       \\
        0                       & 0                       & \frac{2u_1}{\sqrt{15}}  & 0                       \\
        0                       & 0                       & 0                       & \frac{u_1}{\sqrt{5}}    \\
        0                       & 0                       & 0                       & 0
    \end{pmatrix}
    \quad.
\end{proof}
%
The columns of $\mathbf{L}$ are constructed from the coefficient vectors of
each transformed spherical harmonic, which are in turn computed by
multiplying each spherical harmonic by the spherical harmonic decomposition
of the particular limb darkening law. \xxx{A simple algorithm for computing
    $\mathbf{L}$ for limb darkening of any order is given in the link next to
    Equation~(\ref{eq:ld:L}).}

In the presence of limb darkening, we may therefore replace our expression for the
$k^\mathrm{th}$ row of the flux design matrix $\mathcal{A}$ (Equation~\ref{eq:akT})
with
%
\begin{align}
    \label{eq:akTld}
    \mathbf{a}_k^\top = \mathbf{r}^\top \,
    \mathbf{A_1} \,
    \mathbf{L}(\mathbf{u})
    \mathbf{R}_{\hat{\mathbf{x}}}\left(-I\right) \,
    \mathbf{R}_{\hat{\mathbf{z}}}\left(\frac{2\pi}{P}t_k\right) \,
    \mathbf{R}_{\hat{\mathbf{x}}}\left(\frac{\pi}{2}\right)
\end{align}
%
for a given limb darkening coefficient vector $\mathbf{u}$.
